---
title: 'Business Landscape Insights: Key Highlights in `r params$district`'
params:
  district: "Nguyen Binh district"
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: PrettyPDF.tex
documentclass: article
---
<!-- sets fontsize -->
\fontsize{12pt}{14pt}\selectfont

```{r input, echo = FALSE, include = FALSE}
library(ggplot2)
library(tidyverse)
library(stringr)
library(knitr)
library(sf)
library(rmapshaper)


# To handle Vietnamese characters in graphs we set the following chunk options.
knitr::opts_chunk$set(dev = "png", dpi = 200)

# To set parameter manually
#params <- data.frame(district = "Ha Giang City")

# Read tidy_data
data_to_figure <- readRDS("./tidy_data/data_to_figure_workshop.rds") |> 
  filter(District_name == params$district) |> 
  rename(Tên_sản_phẩm = `Tên sản phẩm`)
```


```{r data_1, echo=FALSE}
# Prepare data for figure 1 and accompanying text

#Step 1: Filter so unknown values are not included in figures, prim_prod5_c!="Unknown product"

#step 2: Group by production code
#Step 3: Summarise, divide profit-variable with 1000000000, sum_profit = sum(profit-variable / 1000000000)
#Step 4: Write ungroup(), so variables are no longer grouped
#Step 5: Mutate - create rank-variable using row_number(desc(profit-variable))
#Step 6: Filter on rank<=10

data_1 <- data_to_figure |> 
  # Remove unkown production codes
  filter(!is.na(Tên_sản_phẩm)) |> 
  # Group by production code
  group_by(Tên_sản_phẩm) |>
  # Summarise to sum profit by production
  summarise(sum_profit = sum(profit / 1000000)) |> 
  ungroup() |> 
  # Create new variable 'rank' based on profit
  mutate(rank = row_number(desc(sum_profit))) |> 
  arrange(rank) |> 
  # Filter to 10 largest industries by profit
  filter(rank <= 10) 

```

```{r data_2, warning=FALSE, echo=FALSE, include=FALSE}
# Prepare data for figure 2 and accompanying text

#Step 1: Filter so unknown values are not included in figures, prim_prod5_c!="Unknown product"
#step 2: Group by production code
#Step 3: Mutate, divide profit-variable with 1000000000, sum_profit = sum(profit-variable / 1.000000000)
#Step 4: Write ungroup(), so variables are no longer grouped
#Step 5: Mutate - create rank-variable using row_number(desc(profit-variable))
#Step 6: Filter on rank<=10
#step 7: Group by production code again
#step 8 summarise each emplyment variable like sum_employ_end = sum(no_employ_end)
#step 9 make long data using pivot_longer
#step 10 make labels for each employment variables using ifelse()

data_2 <- data_to_figure |>
  filter(!is.na(Tên_sản_phẩm)) |>  #1
  group_by(Tên_sản_phẩm) |> #2
  mutate(sum_profit = sum(profit) / 1000) |> #3
  ungroup() |> #4
  mutate(rank = dense_rank(desc(sum_profit))) |> #5
  filter(rank <= 10) |> #6
  group_by(Tên_sản_phẩm, rank) |> #7
  summarise(sum_total = sum(n_employee),
            sum_female = sum(n_female_employee),
            sum_nonpaid = sum(n_nonpaid_employee),
            sum_ss = sum(n_employee_ss)) |> #8
  pivot_longer(cols = c(sum_total, 
                        sum_female, 
                        sum_nonpaid, 
                        sum_ss), #9
               names_to = "employee_type",
               values_to = "n_employee")
```

```{r, echo=FALSE}
#Calculate for text here

#Example:
# Total number employed in district
N_employ_total <- data_to_figure |> 
  summarise(N = sum(n_employee)) |> 
  mutate(N = format(N, 
                    big.mark = ".", 
                    decimal.mark = ",",
                    scientific = FALSE)) |> 
  pull(N) 

N_female_total <- data_to_figure |> 
  summarise(N = sum(n_female_employee)) |> 
  mutate(N = format(N, 
                    big.mark = ".", 
                    decimal.mark = ",",
                    scientific = FALSE)) |> 
  pull(N)

N_companies_total <- data_to_figure |> 
  summarise(N = n()) |> 
  mutate(N = format(N, 
                    big.mark = ".", 
                    decimal.mark = ",",
                    scientific = FALSE)) |> 
  pull(N)

largest_industry1 <- data_1 |> 
  filter(rank == 1) |>
  mutate(sum_profit = format(sum_profit, 
                             big.mark = ".", 
                             decimal.mark = ",",
                             scientific = FALSE))

largest_industry2 <- data_1 |> 
  filter(rank == 2) |>
  mutate(sum_profit = format(sum_profit, 
                             big.mark = ".", 
                             decimal.mark = ",",
                             scientific = FALSE))

largest_industry3 <- data_1 |> 
  filter(rank == 3)|>
  mutate(sum_profit = format(sum_profit, 
                             big.mark = ".", 
                             decimal.mark = ",",
                             scientific = FALSE))


```

\subsection{Introduction}
This minireport provides an overview of the business climate for the district of`r params$district`. There are currently `r N_employ_total` people employed in the district, of these `r N_female_total` are women. 

The three largest industries in `r params$district` district by profit are `r largest_industry1$Tên_sản_phẩm`, `r largest_industry2$Tên_sản_phẩm`, and `r largest_industry3$Tên_sản_phẩm`. The combined profit of companies in the largest industry, `r largest_industry1$Tên_sản_phẩm`, was `r largest_industry1$sum_profit` mil. VND. 

```{r, echo=FALSE}
#Calculate numbers for text before first plot

# Calculate mean profit for companies
profit_summary <- data_to_figure |> 
  summarise(mean = mean(profit),
            q1   = quantile(profit, 0.25),
            q3   = quantile(profit, 0.75)) |> 
  mutate(mean = format(mean, big.mark = ".", decimal.mark = ","),
         q1 = format(q1, big.mark = ".", decimal.mark = ","),
         q3 = format(q3, big.mark = ".", decimal.mark = ","))

no_profit <- data_to_figure |> 
  filter(profit <= 0) |> 
  summarise(N = n()) |> 
  pull(N)

```

\subsection{Profit before tax by industry}

The companies of `r params$district` had an average profit of `r profit_summary$mean` VND. With a lower quartile of `r profit_summary$q1` VND and an upper quartile of `r profit_summary$q3` VND. Of the `r N_companies_total` companies in the province, `r no_profit` had no or negative profit. 


```{r,warning=FALSE, results='asis', echo=FALSE, fig.height=4, fig.width=9}

# Print figure 1
ggplot(data = data_1) +
  geom_col(aes(x = reorder(str_wrap(Tên_sản_phẩm, width=45), -rank),
               y = sum_profit), 
           position = "dodge", 
           fill = "forestgreen") + #try looking here for color inspiration: https://www.nceas.ucsb.edu/sites/default/files/2020-04/colorPaletteCheatsheet.pdf
  coord_flip() + #Flips x and y axis
  theme_minimal() +#just one of many themes, try googling "ggplot themes"
  xlab("Production Category") +
  ylab("Total profit before tax") +
  geom_text(mapping = aes(x = reorder(str_wrap(Tên_sản_phẩm, width=45), -rank),
                          y = sum_profit,
                          label = format(round(sum_profit, 0), big.mark = ".", decimal.mark = ".")),
            position = position_dodge(width = 0),
            hjust = "inward")

```

\vspace{0cm}
\subsection{Employment}

```{r, echo=FALSE}
#calculate numbers for using in text before second plot
production_by_employee <- data_to_figure |> 
  filter(!is.na(Tên_sản_phẩm)) |> 
  group_by(Tên_sản_phẩm) |> 
  summarise(total = sum(n_employee)) |> 
  mutate(rank = dense_rank(desc(total)))

largest_employer1 = production_by_employee |> 
  filter(rank == 1) |> 
  mutate(total = format(total, 
                        big.mark = ".", 
                        decimal.mark = ",",
                        scientific = FALSE))

largest_employer2= production_by_employee |> 
  filter(rank == 2) |> 
  mutate(total = format(total, 
                        big.mark = ".", 
                        decimal.mark = ",",
                        scientific = FALSE))

largest_employer3 = production_by_employee |> 
  filter(rank == 3) |> 
  mutate(total = format(total, 
                        big.mark = ".", 
                        decimal.mark = ",",
                        scientific = FALSE))

top3_ratio = production_by_employee |> 
  mutate(top3 = ifelse(rank <= 3, TRUE, FALSE)) |> 
  group_by(top3) |> 
  summarise(group_total = sum(total)) |> 
  ungroup() |> 
  mutate(share_employed = round((group_total / sum(group_total)) * 100, 1))

```

The largest employers by production category in `r params$district` are `r largest_employer1$Tên_sản_phẩm`, `r largest_employer2$Tên_sản_phẩm` and `r largest_employer3$Tên_sản_phẩm`. 



```{r, warning=FALSE, results='asis', echo=FALSE, fig.height=5, fig.width=9}
# Print figure 2
# There are almost no observations that have unpaid employees, so we remove
# these rows to avoid empty columns.
data_2_paid <- data_2 |> 
  filter(employee_type != "sum_nonpaid")

ggplot(data = data_2_paid) +
  geom_col(aes(x = reorder(str_wrap(Tên_sản_phẩm, width=45), -rank), 
               y = n_employee, 
               fill = employee_type),
           position = "dodge") +
  coord_flip() + 
  theme_minimal() +
  scale_fill_manual(values = c("#bef7ff", "#6db0ff", "#458cff"))+
  labs(title = "Number of employees by type and production category",
       fill = "Employee type") +
  xlab("Production") +
  ylab("Number of employees")
```

```{r, echo = FALSE, results = 'asis'}
profit = 3000

if(profit > 0){
  sentence = str_c("The profit is ", profit, ".")
} else{
  sentence = str_c("The loses are ", profit, ".")
}

cat(sentence)

```

\subsection{Net Revenue of `r params$district` compared to other districts in province}
```{r, echo = FALSE, results = 'asis'}

# We need to adjust names to match names from map to the names in data
matched_district_name = params$district |>
  tolower() |> 
  str_remove(" district") |> 
  str_remove(" city") |> 
  str_to_title()

data_to_map = readRDS("./tidy_data/data_to_figure.rds") |> 
  group_by(District_name) |> 
  summarise(`Total Revenue` = sum(Net_rev / 1000000000),
            .groups = "drop") |> 
  mutate(new_name = tolower(District_name),
         new_name = str_remove(new_name, " district"),
         new_name = str_remove(new_name, " city"),
         new_name = str_to_title(new_name)) |> 
  select(-District_name)

shp_in = read_sf(dsn = "./input/shape", layer = "vnm_admbnda_adm2_gov_20201027") |> 
  mutate(ADM2_EN = ifelse(ADM2_EN == "Thong Nong", "Ha Quang", ADM2_EN)) |> 
  group_by(ADM1_EN, ADM2_EN) |> 
  summarise(geometry = st_union(geometry),
            .groups = "drop") |> 
  filter(ADM1_EN %in% c("Bac Kan", "Cao Bang", "Ha Giang"))

match = shp_in |> 
  left_join(data_to_map, join_by(ADM2_EN == new_name)) |> 
  ms_simplify(keep = 0.6)

current_province = match |> 
  filter(ADM2_EN == matched_district_name) |> 
  pull(ADM1_EN)

province_to_map = match |> 
  filter(ADM1_EN == current_province)

district_to_highlight = match |> 
  filter(ADM2_EN == matched_district_name)

ggplot(data = province_to_map) +
  geom_sf(aes(fill = `Total Revenue`), color = "white", lwd = 0.5) +
  geom_sf(data = district_to_highlight, aes(color = ADM2_EN), fill = NA, lwd = 1) +
  scale_fill_steps(n.breaks = 10) +
  guides(color = "none") +
  theme_void()
```


